---
title: "Biden Transition Analysis"
date: December 20, 2020
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: cerulean
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(DT)
library(wrangle)
library(tidyverse)

newnames <- readRDS("~/GITREPSITORY/gw_r_assignment_transition/processed_data/newnames.rds")
staff_data_scraped <- readRDS("~/GITREPSITORY/gw_r_assignment_transition/processed_data/staff_data_scraped.rds")

```

Agency Review Teams  {.tabset}
===============================================================================================================
To filter, click on the boxes at the top of the columns. To sort, use the use/down arrows by the column name.

Row {data-height=1000}
---------------------------------------------------------------------------------------------------------------

### Agency Review Teams

```{r, Include = FALSE}

newnames_table1 <-newnames %>%
  select(name, agency, team_lead, on_multiple_teams, most_recent_employment, source_of_funding, -idstring, -namestring)%>%
  rename(
    'Name' = name,
    'Agency' = agency,
    'Team Lead' = team_lead,
    'On Multiple Teams' = on_multiple_teams,
    'Most Recent Employment' = most_recent_employment, 
    'Source of Funding' = source_of_funding)

  datatable(newnames_table1,
          rownames = FALSE, 
          filter = "top", 
          extensions = 'Buttons',
          options = list(searchHighlight = TRUE, bpaginate = FALSE, dom = 'Bfrtip',
                         buttons = c('copy', 'csv', 'excel', 'print')))
 
```

White House Senior Staff {.tabset}
===============================================================================================================
To filter, click on the boxes at the top of the columns. To sort, use the use/down arrows by the column name.

Row {data-height=1000}
---------------------------------------------------------------------------------------------------------------

### White House Senior Staff

```{r, Include = FALSE}
 Newstaff_table1 <-staff_data_scraped %>%
  select(name, title, -link, -idstring)%>%
  rename(
    'Name' = name,
    'Title' = title, 
    )
  
  datatable(Newstaff_table1,
          rownames = FALSE, 
          filter = "top", 
          extensions = 'Buttons',
          options = list(searchHighlight = TRUE, bpaginate = FALSE, dom = 'Bfrtip',
                         buttons = c('copy', 'csv', 'excel', 'print')))


```



Agency Review Teams Changes 
========================================
To filter, click on the boxes at the top of the columns. To sort, use the use/down arrows by the column name. 

Row {data-height=1000}
-----------------------------------------------------------------------

### Agency Review Teams Changes

```{r}
agencycount_compare %>%
  filter(change > 0)%>%
  gt() %>%
  tab_header(
    title = "Total People Appointed to Each Agency Team & Change from Previous"
  ) %>%
    cols_label(
      agency = "Agency",
      current_count = "Current Count",
      previous_count = "Previous Count",
      change = "Change"
    )

```

White House Senior Staff 
========================================
To filter, click on the boxes at the top of the columns. To sort, use the use/down arrows by the column name. 

Row {data-height=1000}

### White House Senior Staff

```{r}
stafftotal_current <- staff_data_current %>%
  tally(n= "Total People Currently Named to WH Senior Staff")


stafftotal_previous <- staff_data_previous %>%
  tally(n = "Total People Previously Named to WH Senior Staff")

staffcountcompare <- merge(stafftotal_current, stafftotal_previous, all=TRUE)
staffcountcompare

staffcountcompare %>%
  gt() %>%
  tab_header(
    title = "Total People Currently Named to Senior Staff vs. Previous Count"
  )

```

